### 2009-08-16 papers/SBMF2009/Presentation/content/1_introduction.tex
Praticamente final

\begin{itemize}[<+->]
  \item We developed libraries of hardware models%.The modelling is builded using some  developed libraries
  \item The libraries have common concepts that can be used to others platforms of 8 or 16 bits
  \item Utilities of this formal model:
  \begin{itemize}
    \item Documentation
    \item Simulation
    \item The formal verification until the assembly level
    \item A possible support to verify the Z80 design
    	\item Reference for verification of Z80 hardware implementations

>>>>

\begin{itemize}[<+->]
  \item We developed libraries with definitions of hardware and integer types
	%.The modelling is builded using some  developed libraries
  \item The libraries have common concepts that can be used to others platforms of 8 or 16 bits
  \item Utilities of this formal model:
  \begin{itemize}
    \item Documentation
    \item Simulation
    \item Reference for verification of Z80 hardware implementations 
    \item The formal verification to the assembly level
    %\item A possible support to verify the Z80 design
